---
title: "Appendix: Essays on Measuring Credit and Property Prices Gaps"
author: "Nam Nguyen"
institute: "UWM"
short-institute: "UWM"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  beamer_presentation:
    theme: "default"
    colortheme: "default"
    fonttheme: "default"
    keep_tex: true
    slide_level: 2
    includes:
      in_header: preamble.tex
    toc: false
---
# Appendix

## Empirical Results
### Extended Models Regression Results: United States

```{r, echo=FALSE, message=FALSE}
  options(kableExtra.latex.load_packages = FALSE)
  options(knitr.table.format = "pandoc")
  library('kableExtra')
  library(dplyr)
  library(knitr)

  country='US'
  filepath=sprintf('../../HPCredit/Regression/RegCombPercentile_%s.csv',country)
  df<-read.csv(filepath, sep = ",", header=FALSE)

  #rownames(df) <- df[,1]
  #df<-df[,-1]

  df<-df[,-1]
  colnames(df) <- c("Parameters","Median", "[10$\\%$, 90$\\%$]", "Median", "[10$\\%$, 90$\\%$]", "Median", "[10$\\%$, 90$\\%$]")
  options(knitr.kable.NA = '')

  #df = df %>% mutate_if(is.numeric, format, digits=4)

  #https://stackoverflow.com/questions/72388965/aesthetics-of-kable-extra-and-rmardown
  kbl(df, "latex", booktabs = T, digits = c(4, 4, 4, 4, 4, 4, 4), escape=FALSE, linesep=c("", "", "", "\\addlinespace"), row.names=FALSE) %>%
    add_header_above(c(" " = 1, "VAR2" = 2, "VAR2 1-cross lag" = 2, "VAR2 2-cross lags" = 2)) %>%
    footnote(general="US Bayesian method random walk Metropolis-Hasting posterior distribution estimates") %>%
    kable_styling(latex_options=c("striped","scale_down")) %>%
    kable_paper(c("striped")) %>%
    column_spec(c(1,4:5), bold = c(0,0,1,0,0,0,1,0,0,0,0,0,0,0,0))%>%
		gsub(".(begin|end){table.*}", "", ., perl = TRUE)%>%
  	gsub(".centering", "", ., perl = TRUE)
```   

## Empirical Results

### Extended Models Regression Results: United Kingdom 


```{r, echo=FALSE, message=FALSE}
  options(kableExtra.latex.load_packages = FALSE)
  options(knitr.table.format = "pandoc")
  library('kableExtra')
  library(dplyr)
  library(knitr)

  country='UK'
  filepath=sprintf('../../HPCredit/Regression/RegCombPercentile_%s.csv',country)
  df<-read.csv(filepath, sep = ",", header=FALSE)

  #rownames(df) <- df[,1]
  #df<-df[,-1]

  df<-df[,-1]
  colnames(df) <- c("Parameters","Median", "[10$\\%$, 90$\\%$]", "Median", "[10$\\%$, 90$\\%$]", "Median", "[10$\\%$, 90$\\%$]")
  options(knitr.kable.NA = '')

  #df = df %>% mutate_if(is.numeric, format, digits=4)

  #https://stackoverflow.com/questions/72388965/aesthetics-of-kable-extra-and-rmardown
  kbl(df, "latex", booktabs = T, digits = c(4, 4, 4, 4, 4, 4, 4), escape=FALSE, linesep=c("", "", "", "\\addlinespace"), row.names=FALSE) %>%
    add_header_above(c(" " = 1, "VAR2" = 2, "VAR2 1-cross lag" = 2, "VAR2 2-cross lags" = 2)) %>%
    footnote(general="UK Bayesian method random walk Metropolis-Hasting posterior distribution estimates") %>%
    kable_styling(latex_options=c("striped","scale_down")) %>%
    kable_paper(c("striped")) %>%
    column_spec(c(1,4:5), bold = c(0,0,1,0,0,0,1,0,0,0,0,0,0,0,0))%>%
		gsub(".(begin|end){table.*}", "", ., perl = TRUE)%>%
  	gsub(".centering", "", ., perl = TRUE)
```   


## Model

### State Space Representation
	
- Transition equation:
	\begin{align}
		\beta_t = F\beta_{t-1} + \tilde{v}_t
	\end{align}
	
- Where the transitory components are:
	
	\begin{align*}
    \begin{bmatrix}
    \tau_{yt} \\
    c_{yt}    \\
    c_{yt-1}    \\
    \tau_{ht} \\
    c_{ht}    \\
    c_{ht-1}  \\
    \mu_{yt} \\
    \mu_{ht}  
    \end{bmatrix}
    =
    %F matrix
    \begin{bmatrix}
    1 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\
    0 & \phi^1_y  & \phi^2_y  & 0 & \phi^{x1}_y & \phi^{x2}_y & 0 & 0\\
    0 & 1 & 0 & 0 & 0 & 0 & 0 & 0\\
    0 & 0 & 0 & 1 & 0 & 0 & 0 & 1\\
    0 & \phi^{x1}_h & \phi^{x2}_h & 0 &\phi^1_h & \phi^2_h  & 0 & 0\\
    0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
    0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\
    0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 
    \end{bmatrix}
    %Bt-1 matrix
    \begin{bmatrix}
    \tau_{yt-1} \\
    c_{yt-1}    \\
    c_{yt-2}    \\
    \tau_{ht-1} \\
    c_{ht-1}    \\
    c_{ht-2}    \\
    \mu_{yt-1} \\
    \mu_{ht-1} 
    \end{bmatrix}
    +
    \begin{bmatrix}
    \eta_{yt} \\
    \varepsilon_{yt}    \\
    0 \\
    \eta_{ht} \\
    \varepsilon_{ht}    \\
    0 \\
    \eta_{\mu yt} \\
    \eta_{\mu ht}
    \end{bmatrix}
    \end{align*}



<!--
## Comparison with other decomposition methods: US
```{r UKrobust, echo=FALSE, out.width='80%'}
knitr::include_graphics('../../HPCredit/Regression/AR_2/Output/graphs/HP_Credit_2graphs_US.pdf')
```

## Comparison with other decomposition methods: UK
```{r USrobust, echo=FALSE, out.width='80%'}
knitr::include_graphics('../../HPCredit/Regression/AR_2/Output/graphs/HP_Credit_2graphs_UK.pdf')
```
-->



## Chapter 2: Measuring Credit Gaps
### Table of Contents
#### Introduction
- Motivation
- Contribution

#### Methodology
- Data
- Empirical Model
- Results

#### Conclusion


## Empirical Results

We perform these estimations recursively to preserve the 1-sided nature of the credit gap. 

Our first estimation sample runs from 1983:Q1-1988:Q4 and saves the last estimate of the cycle. We keep adding one more observation to the estimation sample and keep saving the last observation of the cycle for different methods. 

- This approach provides us with a 1-sided estimate of the credit gap from different methods.

## Credit-to-GDP Ratios
```{r Credit-to-GDP-Ratios, echo=FALSE, out.width='85%'}
knitr::include_graphics('../../HPI-Credit-Trasitory-Forecast/plots/Credit-to-GDP.pdf')
```


## Chapter 3: Identifying Unsustainable Credit Gaps

### Table of Contents
#### Introduction
- Motivation
- Contribution
- Literature Review


#### Methodology
- Data
- Empirical Model
  + Model Selection
  + Model Averaging
  + Weighted gap creation

#### Results

## Literature Review
Beltran (2021) - measured and the performance of BIS Basel credit gap, along with other decomposition methods and optimized the smoothing parameters $\rho$ in those filters to minimize policy loss function. 

\begin{align*}
L_{\theta,\rho}=\alpha TypeI(\theta)+(1-\alpha)TypeII(\theta)|TPR\ge2/3
\end{align*}

- $\theta$ is the optimized threshold that minizes loss function.

Galán (2019) proposed rolling sample of 15 and 20 years when creating one sided cycle.

Drehmann (2021) created Hamilton filter in a panel setting with fixed coefficients on independent variables across countries.


## AUROC 
Each logistic regression with a different gap measurement yields a Area Under Curve (AUC) of receiver operating characteristic value. There is an underlying assumption that the higher the AUC value is the better overall performance of a credit gap is as an EWI. 

- However, the AUC value received some criticism regarding the area on its lower left corner, where the predictive power of the threshold (TPR) is low.

\begin{align*}
AUC = \int_0^1 TPR d(FPR)
\end{align*}

A ROC curve in the EWI setting represents True Positive Rate (TPR) and False Positive Rate (FPR) of different credit gap thresholds indicating a pre-crisis period.

## partial standardised AUROC (psAUROC)

To overcome the issue of unnecessary information included in the full AUC. An approach to estimate partial AUC was proposed by Detken et al (2014) in the early warning literature.

- psAUC can reveal useful additional information as long as the partial area does not become too restricted


## pAUROC (or pAUC)

Beltran (2021) constrainted the policy loss function to TPR $\ge 2/3$ or Type II error rate $< 1/3$. They then estimated the policy loss function value at different points on the ROC curve by assigning different policy preferences $\alpha$.

$\Rightarrow$ In this paper, we propose to restrict the consideration of the ROC curve to TPR $\ge 2/3$, then estimate the psAUC of the restricted ROC curve region instead.

\begin{align}
pAUROC = \int_{\frac{2}{3}}^1 TNR \, d(TPR)
\end{align}

- TNR = 1- FPR
- FPR = Type I error rate, FNR = Type II error rate



## Variable selection (top 23 gaps ranked by psAUC)

```{r varselect, echo=FALSE, warning=FALSE, message=FALSE}
options(kableExtra.latex.load_packages = FALSE)
options(knitr.table.format = "pandoc")
library('kableExtra')
library(dplyr)
library(knitr)
#library(rstudioapi)
#setwd(dirname(getActiveDocumentContext()$path))
#getwd()

filepath='../../3rdPaper/Data/Output/Modelselection_512.csv'
df<-read.csv(filepath, sep = ",", header=TRUE)

#rownames(df) <- df[,1]
name1<- df[,1]
name1<- gsub("_", ".", name1)
name1[which(name1=="c.hp400k")]<-"BIS Basel gap"
df[,1]<-name1

#df<-df[,-1]
df<-df[-c(27:nrow(df)),-c(10:ncol(df))]
#df<-df[-2,]

#colnames(df) <- c("Median", "10pct", "90pct", "Median", "10pct", "90pct", "Median", "10pct", "90pct")

#options(knitr.kable.NA = '')

#df = df %>% mutate_if(is.numeric, format, digits=4)

#kbl(data.frame(x=rnorm(10), y=rnorm(10), x= rnorm(10)), digits = c(1, 4, 4))

kbl(df, "latex", booktabs = T, digits = c(4, 4, 4, 4, 4, 4, 4, 4), escape=FALSE, linesep=c("","", "", "", "\\addlinespace")
      , row.names = FALSE) %>%
  kable_paper("striped") %>%
  #add_header_above(c("Parameters" = 1, "VAR2" = 3, "VAR2 1-cross lag" = 3, "VAR2 2-cross lags" = 3)) %>%
  #footnote(general="UK Bayesian posterior distribution estimates") %>%
  kable_styling(latex_options="scale_down") %>%
  column_spec(5, bold = TRUE) %>% #c(0,0,1,0,0,0,1,0,0,0,0,0,0,0,0))
  gsub(".(begin|end){table.*}", "", ., perl = TRUE)%>%
  gsub(".centering", "", ., perl = TRUE)
```


## Model posterior probability
- $BIC_k = 2log (Bayesfactor_{sk}) = \chi^2_{sk} - df_klog(n)$
- $\chi^2_{sk}$ is the deviance of model K from the the saturated model
  + $\chi^2_{sk} = 2(ll(Ms) - ll(Mk))$
  + $ll(Mk)$ is the log-likelihood of model Mk given data D

###  Alternate deviance measurement
We propose using psAUC instead of log-likelihood in the measurement of deviance. Hence, an alternative BIC value can be estimated at:

\begin{align}
BIC_{alt,k} &= 2log (Bayesfactor_{alt,sk}) \\
&= 2(1000*(psAUC_s-psAUC_k)) - df_klog(n)
\end{align}
- We scaled the psAUC value by 1000 since $0<psAUC<1$. Also, by design, $psAUC_s=1$.

## Posterior distribution of coefficients of interest:

$\beta_j$ is the coefficient of credit gap j ($c_j$) in a logistic regression model k against pre-crisis indicator. When considering a particular $\beta_1$ :

\begin{align*}
p(\beta_1|D, \beta_1\ne 0) = \sum\nolimits_{A_1} p(\beta_1|D,M_k)p'(M_k|D)
\end{align*}


- where $p'(M_k|D)=p(M_k|D)/ pr[\beta_1 \ne 0|D]$
- and $pr[\beta_1 \ne 0|D] = \sum\limits_{A_1} p(M_k|D)$
  + this is the probability that $\beta_1$ is in the averaged model
  + $A_1= \{M_k: k=1,...,K; \beta_1 \ne 0\}$, is the set of models that includes $\beta_1$
   



## Approximation of point estimate:

\begin{align}
\hat{\beta}_1 = E[\beta_1|D, \beta_1\ne 0] = \sum\limits_{A_1} \hat{\beta}_1(k)p'(M_k|D)
\end{align}

$SD^2[\beta_1|D, \beta_1\ne 0] =[\sum\limits_{A_1}[se_1^2(k)+]+\hat{\beta_1}(k)]p'(M_k|D)
- E[\beta_1|D, \beta_1\ne 0]^2$

- Where $\hat{\beta}_1(k)$ and $se_1^2(k)$ are respectively the MLE and standard error of $\beta_1$ under the model $M_k$. (Leamer 1978, p.118; Raftery 1993a)