## Comparison with other Decomposition Methods
In this section, I check the robustness of the model results by comparing the estimated trend-cycle from my multivariate approach with univariate trend-cycle decomposition using different methods. In addition to estimating the correlation between shocks to the permanent and transitory component, the use of a multivariate model, in theory, should also provide us with a  superior measurement of trend and cycle components compared to the univariate models. To test this hypothesis, I also perform trend-cycle decomposition using the univariate models (Figure \@ref(fig:UKrobust) and \@ref(fig:USrobust)). The univariate models include an HP filter model and a univariate VAR(2) UC model. The HP filter method uses an algorithm to smooth the original data series to estimate the trend component and the difference between them, which is the cyclical component. The parameter value $\lambda$ is set at 125,000 as suggested by Hodrick and Prescott and @ravn_adjusting_2002 for the quarterly data corresponding to a cyclical period of 15-17 years. The univariate UC model only uses a single series of either credit to household or house prices index to decompose a stochastic trend component and a cyclical component with the same specification as the multivariate UC model. 
```{r UKrobust, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'Comparing Multivariate UC cycles with alternate decompositions: UK'}
knitr::include_graphics('../../../HPCredit/Regression/AR_2/Output/graphs/HP_Credit_2graphs_UK.pdf')
```
```{r USrobust, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'Comparing Multivariate UC cycles with alternate decompositions: US'}
knitr::include_graphics('../../../HPCredit/Regression/AR_2/Output/graphs/HP_Credit_2graphs_US.pdf')
```
\newpage
The results from Figure \@ref(fig:UKrobust) and Figure \@ref(fig:USrobust) suggest that the estimate of trends and cycles obtained from the multivariate UC model can capture the dynamics of the two variables during the sample period. The two univariate models fail to generate realistic trends and cycle series by ignoring the relationship between the two variables of interest. The HP cycle seems to do very well at remaining stationary, but by doing so, it missed out on capturing the boom of house prices in the US, leading to the Great Recession of 2009. The cycle from the univariate UC model is close to the multivariate counterpart but failed to fully indicate the magnitude of boom and bust in house prices in the UK before and after the crisis. Overall, it is clear from the analysis above that there is a valuable pay-off in utilizing information from extracting permanent and transitory components of credit to household and house prices index to study the dynamics of the two variables. 

